Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
results
Peter Mozes Micky Palindrome Steve Bone-dry Watson

ROI mapping. ROI mapping is a form of feature selection, wherein only a subset of the d-dimensional input space is used. As described in the introduction, ROIs are anatomically defined brain areas classified as relevant by an expert in the field. To reduce the number of features, average voxel values within this regions are taken as input features. As other higher-order features such as the standard deviation, kurtosis and skewness within ROIs did not increase predictability, these were not included in the subsequent analysis.

Principal Component Analysis (PCA). As feature extraction method, we applied PCA. In between subject classification, the input vectors of the PCA should ideally be the standardized Talairach coordinates. As this coordinate system appeared to be inaccurate for this dataset, we were forced to use the voxel indices. Because brain sizes and shapes differ per subject, it is uncertain whether the voxel indices map well onto each other. As a result, the accuracy of the PCA is reduced.

>>>>

ROI mapping. ROI mapping is a form of feature selection, wherein only a subset of the d-dimensional input space is used. As described in the introduction, ROIs are anatomically defined brain areas classified as relevant by an expert in the field. To reduce the number of features, average voxel values within this regions are taken as input features. As other higher-order features such as the standard deviation, kurtosis and skewness within ROIs did not increase predictability, these were not included in the subsequent analysis. ROIs require \textit{a priori} knowledge. When this knowledge is inaccurate, it results a inductive bias.

Principal Component Analysis (PCA). As feature extraction method, we applied PCA. Ideally, the input vectors of the PCA should be the standardized Talairach coordinates, because we are conducting between-subject classification. As this coordinate system appeared to be inaccurate for this dataset, we were forced to use the voxel indices. The problem is that indices of different subjects may not map well onto each other, due to differences in brain size and shape. As a result, the accuracy of the PCA is reduced.
